Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-05-12 main.Rmd
rephrase fig 4 caption

(ref:allFig) Distribution of energy consumption displayed through letter value plots used to illustrate harmonies and clashes: **a** across month-of-year faceted by quarter-of-year; **b** across weekday/weekend faceted by quarter-of-year; **c** across quarter-of-year faceted by weekday/weekend. **a** shows a clash since there are empty combinations. **b** and **c** show harmonies since each quarter include both weekdays and weekends. It can be seen in **b** that for every quarter (mapped to facet), weekend and weekday consumption are fairly similar except for the second quarter.
For example, the letter value D for weekdays mostly corresponds to letter value E for weekends, implying there are lower values of energy consumption during weekdays in the second quarter. This is probably because of lower temperatures in the second quarter compared to the first quarter (summer in Australia). **c** switches the granularities mapped to the x-axis and the facets and helps to compare quarters within weekdays and weekends. For example, the lower D and E letter values are most different across different quarters for weekdays and weekends respectively.
<!-- For example, for weekdays the interquartile range of consumption reduces over the year, whereas this pattern is not true for weekends. -->

>>>>

(ref:allFig) Distribution of energy consumption displayed through letter value plots to illustrate harmonies and clashes and how change in x-axis and facet mappings change emphasis. **c** shown across month-of-year faceted by quarter-of-year is a clash, as there are empty sets. For example, November can never correspond to Quarter 1. **a** shown across quarter-of-year faceted by weekday/weekend do not include any empty sets and hence is a harmony. The same is true for **b**, which shows the same two cyclic granularities as **a** with reverse mapping. There are no empty combination since each quarter contains both weekdays and weekends. In **a**, it is easier to compare across weekday type (x-axis) within a quarter (facet); within quarter 2, more mass occupied the lower tail on the weekends (letter value E with depth 1/8) relative to that of the weekdays (letter value D 1/16). Coversely, **b** exaggerates differences across quarters (x-axis now) within a specific weekday type; within weekends, the lower letter values C and D for the first and forth quarter are higher than the other quarters.
This is probably because of temperatures in those two quarters are higher as they correspond to summer and spring in Australia.

<!-- ; **b** across weekday/weekend faceted by quarter-of-year; **c** across quarter-of-year faceted by weekday/weekend. **a** shows a clash since there are empty combinations. **b** and **c** show harmonies since each quarter include both weekdays and weekends. It can be seen in **b** that for every quarter (mapped to facet), weekend and weekday consumption are fairly similar except for the second quarter. -->
<!-- For example, the letter value D for weekdays mostly corresponds to letter value E for weekends, implying there are lower values of energy consumption during weekdays in the second quarter. This is probably because of lower temperatures in the second quarter compared to the first quarter (summer in Australia). **c** switches the granularities mapped to the x-axis and the facets and helps to compare quarters within weekdays and weekends. For example, the lower D and E letter values are most different across different quarters for weekdays and weekends respectively. -->
<!-- For example, for weekdays the interquartile range of consumption reduces over the year, whereas this pattern is not true for weekends. -->
